Programs Performance Analysis Toolkit

### 2013-09-30 keynote/Keynote.tex
Describe half of method
Finish the method description

	\begin{enumerate}
		\item Perform a series of experiments on measuring time of program execution and form a set, $U$:
			\begin{equation*}
				U = \{ ( X_i, y_i ) \}, X_i = (x_{ij}, i \in [1;m], j \in [1;n])
			\end{equation*}
		$X_i$ --- features vector (CPU frequency, number of rows of processed matrix, etc.), $y_i$ --- response (execution time), $m$ --- number of experiments, $n$ --- number of features
		\seti
	\end{enumerate}

@@

\begin{frame}
	\begin{enumerate}
		\conti
		\item Split the $U$ set into training sample $D$ and test sample $C$ by randomly assigning of 70\% of experiments to $D$
			\begin{eqnarray*}
				D &=& \{d_i | f_{rand}^I(d_i) > 0.3\}, \\
				d_i &=& (X_i, y_i), \\
				f_{rand}^I(d) &\in & [0:1], \\
				i &\in & [1;m], \\
				C &=& U \setminus D
			\end{eqnarray*}
		\seti
	\end{enumerate}
\end{frame}

>>>>

	\begin{enumerate}
		\item Perform a series of experiments on measuring time of program execution and form a set, $U$:
			\begin{equation*}
				U = \{ ( X_i, y_i ) \}, X_i = (x_{ij}, i \in [1;m], j \in [1;n])
			\end{equation*}
		$X_i$ --- features vector (CPU frequency, number of rows of processed matrix, etc.), $y_i$ --- response (execution time), $m$~---~number of experiments, $n$~---~number of features
		\seti
	\end{enumerate}

@@

\begin{frame}
	\begin{enumerate}
		\conti
		\item Split the $U$ set into training sample $D$ and test sample $C$ by randomly assigning of 70\% of experiments to $D$
			\begin{eqnarray}
				D &=& \{d_i \mid f_{rand}^I(d_i) > 0.3\}, \\
				d_i &=& (X_i, y_i), \\
				f_{rand}^I(d) &\in & [0:1], \\
				i &\in & [1;m], \\
				C &=& U \setminus D
			\end{eqnarray}
		\seti
	\end{enumerate}
\end{frame}

\begin{frame}
	\begin{enumerate}
		\conti
		\item Extract features $x_{ik}$
			\begin{eqnarray}
				x_{ik} &=& f(X_i), \\
				X_i' &=& (x_{ij}) , \\
				D' &=& \{ (X_i' , y_i) \}, \\
				i &\in & [1;m], \\
				j &\in & [1;n+r], \\
				k &\in & [n+1;r]
			\end{eqnarray}
			$r$ --- number of additional features (i.e. ''size of input data'')
		\seti
	\end{enumerate}
\end{frame}

\begin{frame}
	\begin{enumerate}
		\conti
		\item Filter the training set $D'$ to remove noise and incorrect measurements
			\begin{equation*}
				D'' = D' \setminus \{ (X_i', y_i) \mid P(X_i', y_i) \}
			\end{equation*}
			$P$ --- experiment selection predicate (we remove all experiments where the measured execution time is less than $t_{min}$)
		\seti
	\end{enumerate}
\end{frame}

\begin{frame}
	\begin{enumerate}
		\conti
		\item Rank the features and select only ones with non-zero importance
			\begin{eqnarray}
				s_j &=& f_{rank}(D''), \\
				j &\in & [1;n], \\
				D''' &=& \{ (X_i', y_i) \mid S_j > 0 \}
			\end{eqnarray}
			$s_j$ --- scalar value of importance of particular feature, $f_{rank}$~---~feature ranking function (we used \textit{MSE}, \textit{Relief F}, \textit{Earth Importance})
		\seti
	\end{enumerate}
\end{frame}

\begin{frame}
	\begin{enumerate}
		\conti
		\item Fit the regression model of 1 of 4 kinds (linear, random forest, Earth, k nearest neighbors)
			\begin{eqnarray}
				M_p &=& \{ f_{pred}, B\} \\
				B &=& f_{fit}(D''), p \in [1;4]
			\end{eqnarray}
			$B$ --- vector of model parameters, $f_{fit}$~---~learning function, $f_{pref}$~---~prediction function (they're defined for each model separately)
		\seti
	\end{enumerate}
\end{frame}

\begin{frame}
	\begin{enumerate}
		\conti
		\item Test the model by \textit{RRSE} metric
			\begin{eqnarray}
				C &=& U \setminus D \\
				  &=& \{ (X_i', y_i) \}, \\
				i &\in & [1;m], \\
				X_i' &=& (x_{ik}), \\
				k &\in & [1;n+r] \\
				\tilde{Y} &=& f_{pred} (\vec{X}, B), \\
				RRSE &=& \sqrt{ \frac{ \sum\limits_{i=1}^m { ( \tilde{y_i}-y_i )^2 } }
				                     { \sum\limits_{i=1}^m { ( y_i - \bar{y} )^2 } } }
			\end{eqnarray}
		$\tilde{y_i}$ --- predicted value of response, $\bar{y}$~---~average value of response in testing sample
		\seti
	\end{enumerate}
\end{frame}
